\documentclass{article}
\usepackage[margin=0.25in]{geometry}% http://ctan.org/pkg/geometry
\usepackage{flowfram}% http://ctan.org/pkg/flowfram
\usepackage{graphicx,lipsum}% http://ctan.org/pkg/{graphicx,lipsum}
\usepackage{anyfontsize}
\usepackage{fontawesome}
\usepackage{xcolor}
\usepackage{tikz}

% Set no indents before paragraphs
\setlength{\parindent}{0in}

% Left column frame
\newdynamicframe[1]{0.30\textwidth}{1\textheight}
  {-5pt}{0pt}[leftcolumn]

% Right column frame
\newflowframe{0.7\textwidth}{1\textheight}
  {0.3\textwidth}{0pt}[rightcolumn]

% Custom color creationg
\definecolor{header-blue}{RGB}{3, 152, 252}

% Custom section header
\newcommand{\rSection}[1] {
  \textcolor{header-blue} {
    \textbf{{\fontsize{0.5cm}{0.45cm}\selectfont \hbox{#1}}} \\
    \rule{0.30\textwidth}{0.1cm}
  }
}

% Custom sub-section header
\newcommand{\rSubSection}[1] {
  \textbf{{\fontsize{0.4cm}{0.45cm}\selectfont \hbox{#1}}}
}

% Custom sub-sub-section header
\newcommand{\rSubSubSection}[1] {
  \textbf{{\fontsize{0.35cm}{0.45cm}\selectfont \hbox{#1}}}
}

% Proficiency Level View
\newcommand\level[2]{%
  \tikz{%
    \ifx#20
    \else
      \foreach \i in {1,...,#2} {
        \filldraw[black!20] (\i ex,0) circle (0.4ex);
      };
    \fi
    \ifx#10
    \else
      \foreach \i in {1,...,#1} {
        \filldraw[black] (\i ex,0) circle (0.4ex);
      };
    \fi
  }
}

\begin{document}

\begin{dynamiccontents*}{leftcolumn}

    % Name
    {\fontsize{40}{50}\selectfont Collin}\par\bigskip
    {\fontsize{40}{50}\selectfont Bolles}\par\bigskip

    % Contact information
    \begin{tabular}{rl}
        \faSend & collinbolles@gmail.com\\
        \faGithub & cbolles \\
        \faLinkedin & collinbolles \\
        \faPhone & (518)441-4927
    \end{tabular} \bigskip \par

    % Summary
    \rSection{Intro}
        Senior Computer Science student graduating May 2022, looking for a full-time
        opportunity starting in Fall 2022. Main interests in embedded and systems
        level programming.
    \par \bigskip

    % Skills Sections
    \rSection{Skills and Proficiency}

    % Languages
    \rSubSection{Languages} \par \bigskip
    \vspace{-10pt}
    \begin{tabular}{p{3cm} l}
        ARM Assembly & \level{1}{5} \\
        C & \level{4}{5} \\
        C\# & \level{3}{5} \\
        C++ & \level{3}{5} \\
        HTML/CSS & \level{4}{5} \\
        Java & \level{5}{5} \\
        JavaScript & \level{3}{5} \\
        Python & \level{5}{5} \\
        Rust & \level{3}{5} \\
    \end{tabular} \par \bigskip

    % Frameworks and Libraries
    \rSubSection{Frameworks and Libraries} \par \bigskip
    \vspace{-10pt}
    \begin{tabular}{p{3cm} l}
        Django & \level{3}{5} \\
        Flask & \level{3}{5} \\
        Mbed & \level{2}{5} \\
        Node.js & \level{3}{5} \\
        React.js & \level{3}{5} \\
        Requests & \level{4}{5} \\
        Spring Boot & \level{3}{5}
    \end{tabular} \par \bigskip

    % Tools and Environments
    \rSubSection{Tools and Environments} \par \bigskip
    \vspace{-10pt}
    \begin{tabular}{p{3cm} l}
        AWS & \level{1}{5} \\
        Azure & \level{2}{5} \\
        Git & \level{4}{5} \\
        Google Cloud & \level{3}{5} \\
        \LaTeX & \level{3}{5} \\
        Linux & \level{4}{5} \\
        Mac OS & \level{4}{5} \\
        Maven & \level{3}{5} \\
        Vim & \level{3}{5} \\
        Windows & \level{3}{5} \\
    \end{tabular}

    % Awards
    \rSubSection{Awards} \par

% Best IoT Hack
\rSubSubSection{Best IoT Hack} $ \cdot $ \textit{Publicis Sapient} \par

% UB Hackathon 3rd Place Award
\rSubSubSection{UB Hacks 3rd Place Award} $ \cdot $ \textit{UB Hackathon Group} \par

% Congressional App Challenge
\rSubSubSection{Congressional App Challenge Winner} $ \cdot $ \textit{NY Congressional District 21} \par

\end{dynamiccontents*}

% Education and degree
\rSection{Education} \par \bigskip
\rSubSubSection{Rochester Institute of Technology} \par
\rSubSubSection{B.S. Computer Science} \par
GPA 3.85/4 \par
Expected Graduation: May 2022 \par

% Employment information
\rSection{Employment} \par

% D3 Engineering
\rSubSubSection{D3 Engineering} $ \cdot $ Engineering Technician \hfill Jan. 2022 to Dec. 2022 \par
\vspace{-10pt}
\begin{itemize}
    \setlength\itemsep{0pt}
    \setlength{\parskip}{0pt}
    \item Developed Linux Kernel drivers for cameras designed for embedded vision on the NVIDIA Jetson platform
    \item Populated Linux device trees for newly designed hardware
    \item Add features to NVIDIA Linux Kernel to expand camera platform capabilities
    \item Solved hardware and software bugs using Linux and hardware analysis tools on custom hardware
    \item Tools and Technology: C, Python, Linux Kernel, Git, Gerrit
\end{itemize}
\vspace{-10pt}

% HTL
\rSubSubSection{Herrick Technology Labs} $ \cdot $ Software Intern \hfill Sep. 2020 to Dec. 2020 \par
\vspace{-10pt}
\begin{itemize}
    \setlength\itemsep{0pt}
    \setlength{\parskip}{0pt}
    \item Worked on an inter-disciplinary team tasked with producing a multi-faceted sensing solution for US military avionics
    \item Wrote libraries to communicate with HTL radio solutions over a range of protocols including TCP over Ethernet and UART
    \item Optimized radio based object tracking algorithm leveraging GPU based hardware acceleration
    \item Tools and Technology: C++, Python, Git, Cuda
\end{itemize}
\vspace{-10pt}

% Blue Spiral
\rSubSubSection{Blue Spiral} $ \cdot $ Software Developer \hfill June 2020 to Aug. 2020 \par
\vspace{-10pt}
\begin{itemize}
    \setlength\itemsep{0pt}
    \setlength{\parskip}{0pt}
    \item Wrote iOS application for on-the-spot employee performance reviews using SwiftUI
    \item Updated existing image processing pipeline to use the newest Azure OCR API
    \item Developed software to detect vegetation levels from done footage
    \item Tools and Technology: C\#, Swift, Python
\end{itemize}
\vspace{-10pt}

% Ball Bowler
\rSubSubSection{Ball Bowler} $ \cdot $ Software Developer \hfill Jan. 2019 to Nov. 2019 \par
\vspace{-10pt}
\begin{itemize}
    \setlength\itemsep{0pt}
    \setlength{\parskip}{0pt}
    \item Designed and developed a UI for a miniature bowling lane
    \item Implementing scoring logic and user interface on a LattePanda single board computer
    \item Captured state of bowling pins using computer vision
    \item Tools and Technology: Java, JavaFX
\end{itemize}
\vspace{-10pt}

% Blue Spiral
\rSubSubSection{Blue Spiral} $ \cdot $ Software Intern \hfill Aug. 2017 to Aug. 2018 \par
\vspace{-10pt}
\begin{itemize}
    \setlength\itemsep{0pt}
    \setlength{\parskip}{0pt}
    \item Developed object detection training pipeline built on top of Tensorflow
    \item Applied object detection pipeline for the detection of unwanted ducks
    \item Incorporated object detection pipeline with the Microsoft Hololens
    \item Tools and Technology: C\#, Python, C++, Tensorflow
\end{itemize}
\vspace{-10pt}

% Valogix
\rSubSubSection{Valogix} $ \cdot $ Software Intern \hfill July 2016 to Nov. 2018 \par
\vspace{-10pt}
\begin{itemize}
    \setlength\itemsep{0pt}
    \setlength{\parskip}{0pt}
    \item Implement a system level automated testing suite for Valogix web application
    \item Produced custom web API incorporated into Valogix's servers for system health information
    \item Developed a web application for keeping track of the over 100 deployed applications
    \item Resolved bugs and incorporated features in the existing Valogix code base
    \item Tools and Technology: Java, Spring, Spring Boot, PostgreSQL, Groovy
\end{itemize}
\vspace{-10pt}

% Activities
\rSection{Activities} \par

% EVT
\rSubSubSection{Electric Vehicle Team}\par
Firmware Lead \hfill May 2020 to Present \par
Firmware Member \hfill Dec. 2018 to May 202
\vspace{-10pt}
\begin{itemize}
    \setlength\itemsep{0pt}
    \setlength{\parskip}{0pt}
    \item Develop a custom software library for developing firmware on EVT produced hardware (EVT-core)
    \begin{itemize}
        \setlength\itemsep{0pt}
        \setlength{\parskip}{0pt}
        \item Produce object oriented based software layed on top of the STM32 Hardware Abstraction Layer (HAL)
        \item Wrote drivers to support various communication protocols in EVT-core including CAN, UART, I2C, and PWM
    \end{itemize}
    \item Designed and developed firmware for the EVT produced battery management system
    \item Added support for CANopen to EVT-core for communication across the motorcycle systems
    \item Develop drivers for communicating with Sendyne GFD, TI battery management chip, and STM32 peripherals
\end{itemize}
\vspace{-10pt}

\end{document}
